\documentclass{amsart}
\usepackage[nohug,heads=littlevee]{diagrams}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage[latin1]{inputenc}
\usepackage{yfonts}
\usepackage{xr-hyper}
\usepackage[plainpages=false,pdfpagelabels]{hyperref}
\usepackage[nobysame,alphabetic]{amsrefs}
\usepackage{palatino}
\usepackage[left=2.2cm,top=3cm,right=2.5cm,bottom=1in,asymmetric]{geometry}
\usepackage{enumitem}


\input{../../commandssubsub}

\title{Math 3311, Fall 2025: Homework 7}

\begin{document}
\maketitle

For a prime $p$, a \defnword{Sylow $p$-subgroup} of a finite group $G$ is a $p$-subgroup $P\leq G$ such that $p\nmid |G/P|$. We have already seen Sylow Theorem A, which basically tells us that Sylow $p$-subgroups always exist. Here are the remaining two:

\begin{introthm}
[Sylow theorem B]
Let $G$ be a finite group and let $\mathrm{Syl}_p(G)$ be the set of Sylow $p$-subgroups of $G$. Then $G$ acts \emph{transitively} on $\mathrm{Syl}_p(G)$ via conjugation.
\end{introthm}

\begin{introthm}
[Sylow theorem C]
Let $n_p$ be the number of Sylow $p$-subgroups of a finite group $G$. Then:
\begin{enumerate}
	\item $n_p$ divides $[G:P]$ for any Sylow $p$-subgroup $P\leq G$.
	\item $n_p\equiv 1 \pmod{p}$.
\end{enumerate}
\end{introthm}	

\begin{definition}
	A group $G$ is \defnword{simple} if it has no non-trivial, proper \emph{normal} subgroups.
\end{definition}


\begin{enumerate}[itemsep=0.15in]

\item Show that no group of order $100$ or $150$ is simple.

\emph{Hint: What can you say about the Sylow $5$-subgroups in both cases?}

Let $G$ be an arbitrary group of order 100. Let $P\in\mathrm{Syl}_5(G)$, which we know exists by Sylow A
By Sylow C, $|\mathrm{Syl}_5(G)|=n_5\mid[G:P]=100/25=4$ and $|\mathrm{Syl}_5(G)|=n_5\equiv1\pmod{5}$. The only $n_p$ satisfying this is $n_p=1$. So $P$ is a unique Sylow $p$-subgroup. Therefore $P$ is normal, and $G$ cannot be simple

Now, Let $H$ be an arbitrary group of order 150. Let $Q\in\mathrm{Syl}_5(G)$, which we know exists by Sylow A. Again, by Sylow C, $|\mathrm{Syl}_5(H)|=m_5\mid[G:Q]=150/25=6$ and $|\mathrm{Syl}_5(H)|=m_5\equiv1\pmod{5}$. The only $m_p$ satisfying this is $m_p=1$. So $Q$ is normal, and $H$ cannot be simple.

\vspace{0.2in}

\item Show that any simple finite \emph{abelian} group is isomorphic to $\Int/p\Int$ for some prime $p$.

\emph{Hint: Consider Sylow $p$-subgroups for various primes $p$. You might also want to use something from Homework 4.}



\vspace{0.2in}

\item Let $G$ be a group and $H\leq G$ be a subgroup. Consider the action of $H$ on the set of cosets $G/H$ via left multiplication. Show that we have
\[
	(G/H)^H = N_G(H)/H\subset G/H.
\]

\[
X^G = \{x\in X:\; g\cdot x = x\text{ for all $g\in G$}\}.
\]

$(G/H)^H=\{gH\in G/H:\;\forall g'\in G,g'\cdot gH=gH\}$





\vspace{0.2in}

\item Let $G$ be a finite group, $H\unlhd G$ a normal subgroup and $P\in \mathrm{Syl}_p(H)$ a Sylow $p$-subgroup of $H$. Show that $G = HN_G(P)$.

\emph{Hint: Note that, if $g\in G$, then $gPg^{-1}$ is also in $\mathrm{Syl}_p(H)$.}

\item Let $G$ be a finite group with $P\in \mathrm{Syl}_p(G)$. Show that, for any subgroup $M\leq G$ containing $N_G(P)$, we have $M = N_G(M)$. 

In other words, every subgroup containing $N_G(P)$ is its own normalizer.

\emph{Hint: Note that $M$ is normal in $N_G(M)$, and apply the previous problem.}

\vspace{0.2in}

\item Let $G$ be a simple group of order $60$, and let $n_2$ be the number of Sylow $2$-subgroups of $G$.
\begin{enumerate}
	\item Show that $n_2 = 5$ or $n_2 = 15$.
	\item If $n_2 = 15$, show that there exist two distinct Sylow $2$-subgroups $P_1$ and $P_2$ of $G$ such that 
\[
	|P_1\cap P_2| = 2.
\]
\end{enumerate}

\emph{Hint: For part (b), think about the possibilities for $n_5$, and what this says for how many elements can be contained in the union of all Sylow $2$-subgroups.}


\item Let $G$ be as in the previous problem. Suppose that one of the following is true:
\begin{enumerate}
	\item $n_2 = 5$;
	\item $G$ admits a subgroup $H\leq G$ of index $5$.
\end{enumerate}
Show that $G$ is isomorphic to a subgroup of $S_5$ of index $2$.


\item With the same notation as the previous two problems, suppose that $n_2 = 15$, and let $P_1,P_2\in \mathrm{Syl}_2(G)$ be two Sylow $2$-subgroups such that $|P_1\cap P_2| = 2$. Show that the normalizer $N_G(P_1\cap P_2)$ has index $5$ in $G$. Conclude that any simple group $G$ of order $60$ is isomorphic to a subgroup of $S_5$ of index $2$.

\emph{Hint: Note that both $P_1$ and $P_2$ are contained in $N_G(P_1\cap P_2)$.}


\item Suppose that we have $n,m\in \Int$ and consider the homomorphism
\[
\Int \xrightarrow{a\mapsto (a,a)}\Int/n\Int\times \Int/m\Int.
\]
\begin{enumerate}
	\item Show that the kernel of this homomorphism is generated by the least common multiple of $n$ and $m$.
	\item Show that the image of the homomorphism contains $d\Int/n\Int \times d\Int/m\Int$ where $d = \mathrm{gcd}(n,m)$.
	\item Conclude that, if $n$ and $m$ are relatively prime, there is a natural isomorphism of groups
\[
\Int/nm\Int \xrightarrow{\simeq}\Int/n\Int\times\Int/m\Int.
\]

\end{enumerate}

\end{enumerate}

\end{document}